Red-Giant Hot Jupiters: Brilliant Radio Emitter?

### 2015-04-20 ms.tex
equivalent distance for RGHJs are corrected
Changed affiliation: Project Florida -> Sum

\affil{$^2$Research \& Development, Project Florida Labs,
  New York, NY  10001}

@@

On the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows: 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{\mu_0^2 \mathcal{M}^2}{8\pi^3 m_{\rm p}nv^2} \right)^{1/3}  \\
&=& P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp}
\end{eqnarray}
%%%
In order to compare the canonical hot jupiters and red giant hot jupiters, equation (\ref{eq:Pkinp}) can be re-normalized as 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} 
&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
&\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
\end{eqnarray}
%%%
\memoYF{what is the typical wind velocity of AGB stars?}
Therefore, the jupiters to the AGB stars are intrinsically 50 times as bright as typical hot Jupiters. In other words, we could search for radio signal from these stars in $50^3 = 125000$ times as large volume as the canonical hot jupiters.

>>>>

\affil{$^2$Research \& Development, Sum Labs,
  New York, NY  10001}

@@

On the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows: 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{\mu_0^2 \mathcal{M}^2}{8\pi^3 m_{\rm p}nv^2} \right)^{1/3}  \\
&=& P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp}
\end{eqnarray}
%%%
In order to compare the canonical hot jupiters and red giant hot jupiters, equation (\ref{eq:Pkinp}) can be re-normalized as 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} 
&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
&\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
\end{eqnarray}
%%%
\memoYF{what is the typical wind velocity of AGB stars?}
Therefore, the jupiters to the AGB stars are intrinsically 50 times as bright as typical hot Jupiters. In other words, we could search for radio signal from these stars in $(\sqrt{50})^3 = 353$ times as large volume as the canonical hot jupiters.
